Responses to Reviewer Three

### 2021-05-10 Scripts/Reviews/reviewer_three.Rmd
Almost done!

---
title: "Responses to Reviewer Three"
author: "Juliano Palacios"
date: "03/05/2021"
output: pdf_document
---

@@

- The methods are pretty dense, so I would recommend making sure that all of the results
are really clearly described. In a few places, I found them confusing despite having read
the methods very carefully. Specifically:

 - Pg 6, line 16: Is 23% the proportion of revenue from transboundary stocks? Or the proportion of total fishing revenue? It is not totally clear to me as written. I think it’s the former, in which case line 19 should say “…less than 1% of transboundary fishing revenue” and the legend in Fig. 2A should read “% of transboundary fishing revenue.”

@@

@@

- *Response:* We have now included a summarized version of the methods in the main article.

@@

@@

**Response:** We appreciate the acknowledgement.

@@

@@

**Response:** THank you for noticing the EEZ centroids. The figure has been corrected and included the figure in the main text.

@@

**Response:** We understand (and agree!) with this comment. Unfortunately, this is how the *Science* template is currently distributed.

@@

@@

@@

- Pg 4, Line 11-12: I don’t understand what is meant by “misalignment between fisheries resources allocation and distribution shifts” – language is confusing. Do the authors mean misalignment between fishing effort and stock biomass? Also in this paragraph, I think it would be helpful for the authors to add a couple of sentences of explanation for why transboundary stocks are more likely to be over-exploited.

@@

@@

- *Response:* Thank you for noticing. We have removed the repeated text.

@@

- *Response:* Thank you for noticing. Fig. S4 has now a bar legend.

>>>>

---
title: "Responses to Reviewer Three"
output: pdf_document
---

@@

- **Response:** We appreciate the reviewer's comment regarding our method and understand the concern on consider national stocks that become transboundary stocks and *vice versa*, however, these questions have already been responded by Pinsky *et al* (2018) and Oremus *et al.* (2020) and consequently, follow outside the scope of the current paper.

In their 2018 paper, Pinsky *et al* look at how many *new* transboundary species each EEZ of the world will have towards the end of the century under climate change (i.e., national stocks that become transboundary stocks). Indeed, the authors find that "*many of the world’s EEZs are likely to receive one to 12 new, climate-driven transboundary stocks by the end of the century*." On the other hand, Oremus *et al* (2020) "*estimates the number of species exiting national jurisdictions under climate change up to 2100*" concluding that *tropical nations stand to lose the most species under these scenarios.* However, both studies fail to identify changes in the *current* transboundary stock, gap that we look to fill int his paper. Here, we used the species (n = 633) identified by Palacios-Abrantes *et al* (2020) as transboundary and consequently do not have national stocks identified. This was on purpose as the objective of our paper is precisely to look at the impacts of climate change on *current* transboundary species. Addressing the question of entering/exciting stocks would require us to change our initial species list, change our otherwise already complex and long methodology, and likely give the paper a different perspective.

 - Oremus KL, Bone J, Costello C, Molinos JG, Lee A, Mangin T, Salzman J. 2020. Governance challenges for tropical nations losing fish species due to climate change. *Nature Sustainability* 6:1–4.

 - Palacios-Abrantes J, Reygondeau G, Wabnitz CCC, Cheung WWL. 2020. The transboundary nature of the world’s exploited marine species. *Scientific Reports* 10:415–12.

 - Pinsky ML, Reygondeau G, Caddell R, Palacios-Abrantes J, Spijkers J, Cheung WWL. 2018. Preparing ocean governance for species on the move. *Science* 360:1189–1191.

The methods are pretty dense, so I would recommend making sure that all of the results are really clearly described. In a few places, I found them confusing despite having read the methods very carefully. Specifically:

Pg 6, line 16: Is 23% the proportion of revenue from transboundary stocks? Or the proportion of total fishing revenue? It is not totally clear to me as written. I think it’s the former, in which case line 19 should say “…less than 1% of transboundary fishing revenue” and the legend in Fig. 2A should read “% of transboundary fishing revenue.”

 - **Response:** We agree that this was confusing and have modified the initial sentence and adopted the suggestions provided in the revised manuscript. It reads in line **XX** of page **X**: "*From all fisheries targeting transboundary stocks between 2004 and 2010 in the global EEZs, shifting stocks represented on average 23% (s.d. ± 22%) of the yearly revenue (Fig. 2A).*"

@@

 - **Response:** We meant that 59% is the average proportion of the catch that shifts between countries, or more specific, the stocks reponsable for that catch. We have revised the manuscript to clarify this, it reads on line **XX** of page *X*: "*Findings show that by 2030, 59% $\pm$ 17% of the yearly catch from transboundary stocks is projected to change beyond an EEZ’s historic proportion (i.e., between 2004 and 2010; Fig. 4A)*"

@@

- **Response:** The main structure was following the journal's guideline. We have now included a summarized version of the methods in the main article.

@@

*Response:* William, thoughts?

@@

**Response:** We appreciate the acknowledgment on our methods.

@@

- Response: Missing

@@

**Response:** Thank you for noticing the misplace of the EEZ centroids. The figure has been corrected and included the figure in the main text (It is now Fig. 1). The open red circles are located in the bottom panel (B) in each time step where the future distribution overpasses the natural variability.

@@

**Response:** We understand (and agree!) with this comment. Unfortunately, this is how the *Science* template was distributed to us.

@@

**Response:** Thank you, we have adopted the suggested approach. You will read in line 14 of page 1: "*Using global climate-fisheries model simulations, we show that 78% the world’s international boundaries will experience a shifting transboundary stock by 2030*".

@@

- **Response**: We agree with this observation and have modified the revised manuscript to reflect it.

@@

- Pg 4, Line 11-12: I don’t understand what is meant by “misalignment between fisheries resources allocation and distribution shifts” – language is confusing. Do the authors mean misalignment between fishing effort and stock biomass?

- **Response:** We meant misalignment between fishing allocation rules and the stock's biomass this has been clarified in the revised manuscript.

Also in this paragraph, I think it would be helpful for the authors to add a couple of sentences of explanation for why transboundary stocks are more likely to be over-exploited.

- **Response:** We have included one of the examples we referenced, it now reads in line *XX* of page *xxx in the revised manuscript:* *"For example, Pacific salmon (Oncorhynchus sp.) jointly managed by Canada and the U.S. was heavily fished in the early 1990s after a stock shift favored the Alaskan fleet over the Canadian fleet (18).*"

@@

- **Response:** We have included an overall description of the DBEM (including the main equations) in line **XX** of page **X** of the supplemental material.

@@

- **Response:** Thank you for noticing. We have removed the repeated text.

@@

- **Response:** Thank you for noticing. Both figures 4 (now Fig. 5) and S4 have a bar color legend now.
